Reproduction

### 2024-11-12 pages/reproduction.qmd
feat(reproduction): save times figure to png
feat(reproduction): add linestyles and alt legend to time-to-completion non-interactive

# Create list with the dataframes, labels and colours, to use for each plot
to_plot = [
    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
    (df_hua, 'Huang et<br>al. 2019', '#228833'),
    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
    (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
    (df_her, 'Hernandez<br>et al. 2015', '#882255'),
    (df_woo, 'Wood et al.<br>2021', '#117733')
]
```

@@

# Loop through and add lines for each reproduction
for x in to_plot:
    success_static(x[0], ax, x[1], x[2])

@@

>>>>

# Create list with the dataframes, labels and colours, to use for each plot
# Include alternative label for article with % reproduced and time
# (rather than names), and a linestyle
to_plot = [
    (
        df_ana,
        'Anagnostou<br>et al. 2022',
        '#882255',
        '100% (1/1), 2h 11m',
        (0, (1, 1))
    ),
    (
        df_woo,
        'Wood et al.<br>2021',
        '#117733',
        '100% (5/5), 3h 50m',
        '--'
    ),
    (
        df_lim,
        'Lim et<br>al. 2020',
        '#4477aa',
        '100% (9/9), 12h 27m',
        '-.'
    ),
    (
        df_kim,
        'Kim et<br>al. 2021',
        '#ccbb44',
        '100% (10/10), 14h 42m',
        ':'
    ),
    (
        df_her,
        'Hernandez<br>et al. 2015',
        '#aa3377',
        '12.5% (1/8), 17h 56m',
        '-'
    ),
    (
        df_joh,
        'Johnson et<br>al. 2021',
        '#66ccee',
        '80% (4/5), 19h 49m',
        (0, (3, 1, 1, 1, 1, 1))
    ),
    (
        df_hua,
        'Huang et<br>al. 2019',
        '#228833',
        '37.5% (3/8), 24h 10m',
        (0, (3, 3, 1, 3, 1, 3))
    ),
    (
        df_sho,
        'Shoaib and<br>Ramamohan<br>2022',
        '#ee6677',
        '94% (16/17), 28h 14m',
        (5, (10, 3))
    )
]
```

@@

# Loop through and add lines for each reproduction
for x in to_plot:
    success_static(x[0], ax, x[1], x[2], ls=x[4])

@@

Version of non-interactive figure used in article:

```{python}
# Create figure object
fig, ax = plt.subplots(figsize=(8, 4))

# Loop through and add lines for each reproduction
for x in to_plot:
    success_static(x[0], ax, label=x[3], colour=x[2], ls=x[4])

# Save figure (to use in article)
plt.tight_layout()
plt.savefig('../images/article_times.png', dpi=300)
```
